Neural Network Language Models for Automatic Speech Recognition

### 2018-12-12 paper/paper.tex
paper: Reflow Xavier Initialization section
paper: Tidy up wording a little on Xavier Initialization
paper: Reflow section on tied weights
paper: Clarify missing word counts in gigaword/wikitext

This dataset is based on articles from Wikipedia, containing 1,756,924 tokens in
the training set, 184,354 tokens in the validation set and 207,080 tokens
in the test set. The combined dictionary for all three sets contains 28,755
unique tokens.

@@

The second dataset we used was Gigaword. This dataset is based on XXX,
containing 110,382,986 tokens in the training set, 549,0454 tokens in the
validation set and XXX tokens in the test set. The combined dictionary
contains XXX unique tokens.

@@

XXX

@@

In all three models we get worse results when implementing Xavier initialization. The perplexity is not modified by much but METEOR, ROUGE and Naive Accuracy are clearly worse. Analysis of the activation function values across training steps would be needed to determine why Xavier initialization wasn't able to improve the results.

>>>>

This dataset is based on articles from Wikipedia, containing 1,205,450 tokens in
the training set, 184,354 tokens in the validation set and 207,080 tokens
in the test set. The combined dictionary for all three sets contains 21,190
unique tokens.

@@

The second dataset we used was Gigaword. This dataset is based on XXX,
containing 8,658,023 tokens in the training set, and 341,317 tokens in the
validation set. The combined dictionary contains 59760 unique tokens.

@@

"five time world champion kwan withdrew from the US figure skating championships
on Wednesday, but will petition US skating officials for the chance to compete
\emph{at the Turin Olympics}."

"US business leaders lashed out wednesday at legislation that would penalize companies
\epmh{for employing illegal immigrants}."

@@

In all three models we get worse results when implementing Xavier initialization. Xavier Initialization does not
affect perplexity that much, but but METEOR, ROUGE and Naive Accuracy performed much worse than the baseline.
Analysis of the activation function values across training steps would be needed to determine why Xavier
initialization wasn't able to improve the results.
